getwd()
library(tidyverse)
library(readxl)
library(writexl)

---
  title: "IITAPedigree"
  author: "Cletus Emmanuel"
  date: "2022-04-13"
  editor_options:
    chunk_output_type: console
---






This R script is useless at the moment, trying to figure out how i can work around the technique using a different method with the script down here. This will just extract the Accessions starting with those prefixes.



Use the remaining 2 R scripts below this one.
```{r}

ag_data = read.csv("IITAPedigree.csv", na = c(" ", ".", "NA"))
head(ag_data)

get_requiredRows = function(pedigree){
  ag_data_filtd = pedigree %>% rowwise() %>%
    filter(startsWith(Accession, prefix = "IITA-TMS") | 
            startsWith(Accession, prefix = "TMS") |
            startsWith(Accession, prefix = "IBA"))
  return(ag_data_filtd)
}

new_data = get_requiredRows(ag_data)

View(new_data)


```


You can work with this, this will get the first two digit of every accession which in our case is the year, and add it to its century, which is a standard representation of "YEAR".


```{r}


adjust_accession_years = function(new_data){
  pedigree = new_data %>% mutate(accession_y = 
              as.numeric(str_extract(Accession, "\\d{2}")))
  
  pedigree_alt = pedigree %>% 
    rowwise() %>%
    mutate(accession_y = ifelse(accession_y > 22, accession_y + 1900,
                                accession_y + 2000))
  return(pedigree_alt)
  
}
ag_data = read.csv("IITAPedigree.csv", na = c(" ", ".", "NA"))
ag_arg = adjust_accession_years(ag_data)
ag_arg
```


After getting the year for all the accessions on a different column, I just need to delete the invalid years, i.e from the accessions that are not IITA, TMS, OR IBA using nested ifelse function. I get those ones and then delete the year. Then i am left with the exact accessions with years i really need. After which i exported into a new csv file.


```{r}

### Check if accession name meets the following conditions
ag_arg$accession_y2 =ifelse(startsWith(as.character(ag_arg$Accession),"IITA-TMS"),
                           ag_arg$accession_y,
                           ifelse(startsWith(as.character(ag_arg$Accession),"TMS"),
                            ag_arg$accession_y,
                          ifelse(startsWith(as.character(ag_arg$Accession),"IBA"),
                            ag_arg$accession_y, NA)))

ag_arg$accession_y2 = ifelse(grepl("SN", ag_arg$Accession), 
                             1+ag_arg$accession_y2, ag_arg$accession_y2)
ag_arg$accession_y = ag_arg$accession_y2
ag_arg = subset(ag_arg, select = -c(accession_y2))
ag_arg
write.csv(ag_arg, file = "new_pedigree.csv", row.names = FALSE)
```